\begin{acknowledgments}

  First and foremost, I'd like to express my deepest gratitude to my advisor Dr. Alvin Lim. I'm grateful for his continuous support, encouragement, and guidance, without which this work would have been impossible. His patience, compassion, and positive altitude have greatly motivated me in the past five years. Dr. Lim has been a fantastic mentor to me in both research and life and I'm truly lucky to have met him.

  My gratitude also goes to Dr. Saad Biaz, Dr. Hari Narayanan, and Dr. Xiao Qin for serving on my advisory committee, and Dr. Shiwen Mao for being my university reader. They have given helpful and insightful advices for my dissertation work.

  I'd like to thank Dr. David Bevly for not only the help and guidance in research projects, but also providing opportunities for me to work with a wonderful multidisciplinary team. Thanks also go to Richard Bishop, Dr. Jim Shurbutt, and Austin Schuh for providing strong support in my research projects.

   This research is supported in part by the \textit{US Federal Highway Administration}, under Contract No. DTFH61-13-H-00019, entitled \textit{Heavy Truck Cooperative Adaptive Cruise Control: Evaluation, Testing, and Stakeholder Engagement for Near Term Deployment}.

  I'm grateful to have my lab-mates who have created a cheerful atmosphere and shared with me the joy of exploration, in particular, Jian Fang, Dr. Seungbae Lee, Dr. Dongjin Kim, Dr. Kanika Grover, James McCracken, Dongsuk Song, Abhishek Kulkarni, Amogh Kashyap, Ethan Mata, Yufei Yan, Kaushik Vedalaveni, Hannah Chappell, Matthew Rhodes, and Jason Perreault. My gratitude also goes to Dr. Shuang Li and Dr. Qing Yang for providing valuable advices and help in my graduate studies. I'd also like to thank the wonderful staff in CSSE, JoAnn Lauraitis, Barbara McCormack, Kecia Hill, Kelly Price, and Michelle Brown.

  It has been a delightful experience working with my colleagues, from whom I have learnt tremendously and never failed to satisfy my curiosity, namely Lowell Brown, Luke Humphreys, Grant Apperson, Dan Pierce, Robert Cofield, Christopher Rose, Amos Smith, Scott Smith, Dr. Joshua Batterson, Andrew Watts, Nicholas Smith, Tianqi Gao Smith, Mikhail Gordon, Shraddha Praharaj, Jeffrey Wayne Nolen, and Willis Walker. In addition, I'd like to thank Jennifer Dukes and other staff at NCAT for making it possible to run real-world truck experiments. Thanks also go to Dennis Wilson and Richard Kent for teaching me how to move semi-trailer trucks.

  My sincere gratitude also goes to Robert Chiniquy, who has been a great friend and an awesome mentor to me. I'm also grateful to have met Paul Querna, Russell Haering, Ryan Phillips, and Justin Gallardo. These people together have shaped my journey into the software industry.

  I'd like to thank all the great people I've met in Auburn, especially, Jue Wang, Dr. Liang Tang, Yusheng Ding, Shuwei Zhang, Jiayi Xu, Yawei Chen, Dr. Qing Dai, Rong Zhang, Rui Guo, Selena Guo, Kang Sun, Dr. Chih-Jye Wang, Zhitao Gong, Haoran Zhang, Junchao Wei, Mary Olson, Orba Lee Humphrey, Ken Thomas, and Will Abercrombie, for allowing me to have a memorable and beautiful experience in Auburn.

  Above all, none of these would have been possible without the support from my family. I'm grateful for my parents Yan Xiong, Lili Gao, and my grandparents Yingqing Xiong and Sufang Shu, for their dedication, love, and support throughout my life. My gratitude also goes to Yunfeng Bai, who has inspired and supported me like family. I'm deeply thankful that my grandfather Yingqing Xiong developed my initial interest in engineering and computer systems. He was an remarkable engineer and I'd be happy if I become half as good as him.

  Last but not least, my sincere gratitude goes to my wife Xinyu Zhao, for her love, support, and always being there for me in the good and bad times. Life is a beautiful journey and I'm charmed to have her in my life. 

\end{acknowledgments}

